J. Derek Tucker

### 2022-12-21 index.qmd
update description

---
title: "J. Derek Tucker"
subtitle: "Distinguished Member of Technical Staff, Sandia National Laboratories\\ Adjunct Professor, Department of Statistics, University of Illinois"
image: images/me.jpg
about:
  template: trestles
  links:
    - icon: linkedin
      url: "https://linkedin.com/in/derek-tucker-04247818"
    - icon: github
      url: "https://github.com/jdtuck"
    - icon: google
      url: "https://scholar.google.com/citations?user=1jdvTZwAAAAJ&hl=en"
    - icon: file-pdf
      url: "http://arxiv.org/a/tucker_j_1"
    - icon: bi-envelope
      url: "mailto:jdtuck@sandia.gov"
    - text: CV
      href: "Docs/JDT_CV.pdf"
resources:
    - "Docs/JDT_CV.pdf"
---
::: {.column-page}

>>>>

---
title: "J. Derek Tucker"
description: | 
             | *Distinguished Member of Technical Staff*, Sandia National Laboratories 
             | *Adjunct Professor*, Department of Statistics, University of Illinois
image: images/me.jpg
about:
  template: trestles
  links:
    - icon: linkedin
      url: "https://linkedin.com/in/derek-tucker-04247818"
    - icon: github
      url: "https://github.com/jdtuck"
    - icon: google
      url: "https://scholar.google.com/citations?user=1jdvTZwAAAAJ&hl=en"
    - icon: file-pdf
      url: "http://arxiv.org/a/tucker_j_1"
    - icon: bi-envelope
      url: "mailto:jdtuck@sandia.gov"
    - text: CV
      href: "Docs/JDT_CV.pdf"
resources:
    - "Docs/JDT_CV.pdf"
---

::: {.column-page}
